### 2020-04-30 final_report/methodology.tex
change 'learn' to 'train'

The goal of the last two experiments is to exploit the information gathered by
hyperparameter tuning to investigate scaling properties. In
the third experiment, the 20~best-performing hyperparameter choices of each family
(in $R^2$) are used to learn surrogates using progressively larger training sets. Following
that, the fourth experiment aims to produce surrogates for practical use by
retraining selected well-scaling models to further optimise their properties.

>>>>

The goal of the last two experiments is to exploit the information gathered by
hyperparameter tuning to investigate scaling properties. In
the third experiment, the 20~best-performing hyperparameter choices of each family
(in $R^2$) are used to train surrogates using progressively larger training sets. Following
that, the fourth experiment aims to produce surrogates for practical use by
retraining selected well-scaling models to further optimise their properties.

### 2020-04-30 final_report/results.tex
change 'learn' to 'train'

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
experiments~2-3, we utilised the best-performing hyperparameter
assignments and training sets of varying sizes. In attempts to satisfy
goals~(i) and~(ii) within cross-validation setting, our best surrogate
achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
used the entire available set of~\num{500000} datapoints, in attempts to satisfy
goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
using only a set of size~\num{10000}.

>>>>

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
experiments~2-3, we utilised the best-performing hyperparameter
assignments and training sets of varying sizes. In attempts to satisfy
goals~(i) and~(ii) within cross-validation setting, our best surrogate
achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
goal~(iii) we also trained a more simplified model that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with only a set of size~\num{10000}.
